Manuscript Figures for Genome Biology

### 2018-06-22 manuscript_figures/manuscript_figures.Rmd
Add Supp figure to compare ranks in sim vs casestudies

# generate detailed case study table for creating sim vs cs ranks boxplots
yeastsim.tab <- plotMethodRanks(objs, colLabels = labs, alpha = alpha,
                                 tableOnly = TRUE)
```

>>>>

# generate detailed yeast sim table for creating sim vs cs ranks boxplots
yeastsim.tab <- plotMethodRanks(objs, colLabels = labs, alpha = alpha,
                                 tableOnly = TRUE)
```
